\PassOptionsToPackage{pdfpagelabels=false}{hyperref} 
\documentclass[12pt,a4paper]{moderncv}
\usepackage{lmodern}
\moderncvtheme[blue]{casual}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}
\AtBeginDocument{\recomputelengths}
\nopagenumbers{}
\firstname{Vinay }
\familyname{S Rao}
\mobile{+91-8105607537}
\phone{080-26394412}
\address{63, 22 Main, 12 A Cross, Padmanabhanagar}{Bangalore 560070}
\email{sr.vinay@gmail.com}
\extrainfo{twitter: @vinaysrao, github:\httplink{https://github.com/vinaysrao}}

\begin{document}
\maketitle
\section{Education}
\cventry{2009-(expected)2013}{Bachelor of Engineering, Information Science and Engineering}\newline{Visvesvarayya Technological University}{B.M.S College of Engineering, Bangalore}{GPA:\textit{8.60/10.0}}

\cventry{2007-2009}{Pre University College}{Kumaran PU College, Bangalore}{First class with distinction (95\%)}{}{}

\section{Skills}
\cvlistitem{\small Ability to work with people across countries and cultures.}
\cvlistitem{\small Problem solving.}
\cvlistitem{\small Knowledge of source control management systems like git.}


\section{Technical Skills}
\cvcomputer{Languages}{C,C++,Python,Java,JavaScript,Php,C\#}{}{}
\cvcomputer{Frameworks}{Django,Qt,numpy,scipy,scikitlearn,nltk}{}{}
\cvcomputer{Others}{bash,awk,bf,perl,html,css,ajax}{}{}
\cvcomputer{}{\httplink{https://github.com/vinaysrao}}{}{}

\section{Projects}
\cvline{Academic}{\textbf{Centralized News Feed}}
\cvline{}{\small A simple to use news feed system that can be setup in no time. Includes 
a live news ticker, tag clouds, search( separate from content ), comments. ( Written in Php, ECMA + AJAX, mySQL )}

\cvline{Season of KDE 2011}{\textbf{UI Config Compiler}}
\cvline{}{\small A compiler that converts configuration files written in simple XML, to equivalent
Python script files. Specifically written for PyQt-UI configuration files size. ( Written in C++ )}

\cvline{Google Summer of Code 2012}{\textbf{Save/load system for Gluon}}
\cvline{}{\small Gluon is a game creation and playing engine, written in Qt. I implemented a system to
save and load game states, using scene graphs. Also substantially reduced saved game files' size. ( Coded in C++ )}

\newpage{}

\cvline{Other}{Automated coding judge}
\cvline{}{\small Written in Django, this is a way to easily hold coding competitions, where
users are given unique inputs, and are ranked based on difficulty and speed. ( Python + Django )}

\cvline{Other}{Generic A* search}
\cvline{}{\small A generic implementation of A* search for in-game AI, calculated using any chosen heuristics ( Python )}

\makefooter

\section{Co-curricular activities}
\cvlistitem{\small Open source contributor and developer for KDE}
\cvlistitem{\small Organized Software Freedom Day - 2011 and 2012 at BMSCE}
\cvlistitem{\small Conducted technical workshops and have been instrumental in organizing events for BMSLUG}

\section{Extra-curricular activities}
\cvlistitem{\small Completed senior grade in instrumental Carnatic music (Flute) and performed at many
prestigious events and stages.}
\cvlistitem{\small Coordinator of the music team at BMSCE - won laurels on various occasions}
\cvlistitem{\small Cartooning, swimming, basketball}

\section{Additional information}
\cvline{Date of birth}{15-05-1991}

\end{document}